Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2012-09-18 chi2012.tex
a  few more

Looking at overlap, we notice overall little overlap among records; that is, except for the smallest records (which had few properties to begin with), most of the data records had more unique properties than ones in common with others.  While some of these 'unique records' were primarily for internal, service-specific use (such as service-specific IDs) others were useful properties one would expect to find in a record that were simply not present.  Only one of the music data providers, Spotify, included information about the album(s) that featured a particular song.  Such omissions show us that these data APIs reflect each service provider's own capabilities and internal data representations very specifically, and that integrating data such records from multiple sources could allow more complete and useful representations to be assembled.

@@

Modelling

>>>>

Looking at equivalent properties, we foun overall little overlap among records; that is, except for the smallest records (which had few properties to begin with), most of the data records had more unique properties than ones in common with others.  While some of these 'unique records' were primarily for internal, service-specific use (such as service-specific IDs) others were useful properties one would expect to find in a record that were simply not present.  Only one of the music data providers, Spotify, included information about the album(s) that featured a particular song.  Such omissions show us that these data APIs reflect each service provider's own capabilities and internal data representations very specifically, and that integrating data such records from multiple sources could allow more complete and useful representations to be assembled.

@@

Modelling heterogeneity was also comparatively rare,

Although not included in the table above, we also examined enumerated values for a number of the data sources above.  Field even as simple as ``Gender'' often disagreed in the
